\documentclass{article}
\usepackage{Macros}

\newcommand{\class}[1]{\section{class \texttt{#1}}}
\newcommand{\attribute}[1]{\subsection{\texttt{self.#1}}}
\newcommand{\method}[1]{\subsection{\texttt{self.#1}}}
\newcommand{\function}[1]{\section{\texttt{#1}}}
\newcommand{\argumenta}[1]{\subsection{\texttt{#1}}}
\newcommand{\argumentb}[1]{\subsubsection{\texttt{#1}}}


\begin{document}
\begin{flushleft}

\begin{center}
  Cowbot Documentation: GameState.py
\end{center}
%%%Boost order for orange team is exactly reversed.
%TODO: Reverse boost list if on orange team, so that I can use the same numbers either way.

\class{GameState}
      {

        The class that handles recording the state of the game, including information about all cars, the ball, and the boosts.  Nothing in the \texttt{game\_info} object should be modified after initiation of \texttt{GameState}.



        \attribute{is\_kickoff\_pause}
                  {
                    Boolean.  Is True while the players are free to move during kickoff, but the clock is not yet running.
                  }
        \attribute{kickoff\_position}
                  {
                    String.  Defaults to \texttt{``Other''}, and is set and interpreted by the kickoff code.  Stores which of the five standard kickoff positions the bot is in for a kickoff.  Will be \texttt{``Other''} when not in a kickoff.
                  }
        \attribute{my\_team}
                  {
                    0 or 1.  Is 0 if our bot is on the blue team, is 1 if our bot is on the orange team.
                  }
        \attribute{team\_sign}
                  {
                    +1 or -1.  Is +1 if our bot is on the blue team, is -1 if our bot is on the orange team. This is used to mirror coordinates so that most of the code doesn't depend on which team we're on.
                  }
        \attribute{ball}
                  {
                    \texttt{BallState}.  Stores all information about the ball.
                  }
        \attribute{me}
                  {
                    \texttt{CarState}. Stores all the information about our bot's car.
                  }
        \attribute{my\_index}
                  {
                    Integer.  The index of our bot in the framework's list of game cars.
                  }
        \attribute{teammates}
                  {
                    List.  A list of \texttt{CarState}s for our teammates.
                  }
        \attribute{opponents}
                  {
                    List.  A list of \texttt{CarState}s for our opponents.                    
                  }
        \attribute{big\_boosts}
                  {
                    List.  A list of \texttt{Boostpad}s specifically for the big boosts.  This probably won't get much use in our code, and may be removed later.
                  }
        \attribute{boosts}
                  {
                    List.  A list of all \texttt{Boostpad}s on the field, with index matching the framework's index.
                  }
        \attribute{game\_time}
                  {
                    Float.   The time that has passed since the beginning of the game.
                  }
        \attribute{utils\_game}
                  {
                    \texttt{Game}.  A \texttt{Game} object from RLU.  Mainly used to get the time step and initialize the RLU mechnanics and make them work.  I never interface with it directly for other purposes.
                  }
        \attribute{dt}
                  {
                    Float.  The time elapsed since the last tick.  Used for anything resembling a derivative.
                  }
        \attribute{opponent\_distance}
                  {
                    Float.  The minimum distance from an opponent to the ball in uu.
                  }

      }






\class{Orientation}
      {

        The object that handles all orientation related information for game objects.  Can be used as yaw-pitch-roll or a rotation matrix (eventually add quaternion support as well).  WARNING: Rocket League uses the order Yaw-Pitch-Roll for the orientation of objects, but much of the code here and in the framework uses Pitch-Yaw-Roll instead.


        \attribute{pitch}
                  {
                    Float between $- \frac{\pi}{2}$ and $\frac{\pi}{2}$. Rotation about an object's $y$-axis.
                  }
        \attribute{yaw}
                  {
                    Float between $- \pi$ and $\pi$. Rotation about an object's $z$-axis.
                  }
        \attribute{roll}
                  {
                    Float between $- \pi$ and $\pi$. Rotation about an object's $x$-axis.
                  }
        \attribute{matrix}
                  {
                    List.  A list containing the vectors \texttt{front}, \texttt{left}, and \texttt{up}.  Forms a 3x3 orthogonal matrix (rotation matrix).
                  }
        \attribute{front}
                  {
                    \texttt{Vec3} unit vector.  The vector in the front-facing direction of the object.  First column of the orientation matrix.
                  }
        \attribute{left}
                  {
                    \texttt{Vec3} unit vector.  The vector in the left-facing direction of the object.  Second column of the orientation matrix.
                  }
        \attribute{up}
                  {
                    \texttt{Vec3} unit vector.  The vector in the up-facing direction of the object.  Third and final column of the orientation matrix.
                  }
                  

      }






\function{Ball(packet, team\_sign, state = None)}
         {
           \texttt{packet}: \texttt{GameTickPacket}.  The packet containing all gamestate information.\\
           \texttt{team\_sign}: +1 or -1.  Is +1 if we are on the Blue team, -1 if we are on the Orange team.  This is used to reflect quantities so that the rest of the code is team-independent.\\
           \texttt{state}: A framework ball prediction slice object.\\
           \texttt{Ball} returns a \texttt{BallState} object with the parameters stored in \texttt{state} if specified, otherwise in \texttt{packet}.
         }




\class{BallState}
      {
        \attribute{pos}
                  {
                    \texttt{Vec3}.  The $(x , y , z)$ position of the ball.
                  }
        \attribute{rot}
                  {
                    \texttt{Orientation}.  The \texttt{Orientation} object corresponding to the ball's current 3d orientation. 
                  }
        \attribute{vel}
                  {
                    \texttt{Vec3}.  The $(v_x , v_y , v_z)$ velocity of the ball.
                  }
        \attribute{omega}
                  {
                    \texttt{Vec3}.  The $(\omega_x , \omega_y , \omega_z)$ angular velocity of the ball.
                  }
        \attribute{last\_touch}
                  {
                    Is currently broken in framework.   Also looks broken in the \texttt{GameState} code, or at least is not in terms of CowBot data types.
                  }
        \attribute{hit\_location}
                  {
                    Is currently broken in framework.   Also looks broken in the \texttt{GameState} code, or at least is not in terms of CowBot data types.                    
                  }


        \method{copy\_state}
               {
        \argumentb{pos}
                  {
                    \texttt{Vec3}.  The $(x , y , z)$ position of the ball.
                  }
        \argumentb{rot}
                  {
                    \texttt{Orientation}.  The \texttt{Orientation} object corresponding to the ball's current 3d orientation. 
                  }
        \argumentb{vel}
                  {
                    \texttt{Vec3}.  The $(v_x , v_y , v_z)$ velocity of the ball.
                  }
        \argumentb{omega}
                  {
                    \texttt{Vec3}.  The $(\omega_x , \omega_y , \omega_z)$ angular velocity of the ball.
                  }                 
               }

      }







\function{Car}


\class{CarState}

      {
        \attribute{pos}
                  {
                    \texttt{Vec3}.  The $(x , y , z)$ position of the car.
                  }
        \attribute{rot}
                  {
                    \texttt{Orientation}.  The \texttt{Orientation} object corresponding to the car's current 3d orientation. 
                  }
        \attribute{vel}
                  {
                    \texttt{Vec3}.  The $(v_x , v_y , v_z)$ velocity of the car.
                  }
        \attribute{omega}
                  {
                    \texttt{Vec3}.  The $(\omega_x , \omega_y , \omega_z)$ angular velocity of the car.
                  }
        \attribute{demo}
                  {
                    Boolean.  True if the car is currently off the field as a result of being demoed.
                  }
        \attribute{wheel\_contact}
                  {
                    Boolean.  True if the car has wheel contact.  Can be with the ground, walls, ceiling, ball, or another car.
                  }
        \attribute{supersonic}
                  {
                    Boolean.  True if the car is supersonic.
                  }
        \attribute{jumped}
                  {
                    Boolean.  True if the car has jumped and has not yet regained wheel contact.
                  }
        \attribute{double\_jumped}
                  {
                    Boolean.  True if the car has double jumped, including dodges, and has not yet regained wheel contact.
                  }
        \attribute{boost}
                  {
                    Float.  The amount of boost that the car has.
                  }
        \attribute{index}
                  {
                    Integer.  The index of the car in the framework's game\_cars list.
                  }
        \attribute{jumped\_last\_frame}
                  {
                    Boolean.  True if the car input jump on the previous tick.  Only for our car, since we aren't allowed to look at the inputs of other cars.
                  }

        \method{copy\_state}
               {
        \argumentb{pos}
                  {
                    \texttt{Vec3}.  The $(x , y , z)$ position of the car.
                  }
        \argumentb{rot}
                  {
                    \texttt{Orientation}.  The \texttt{Orientation} object corresponding to the car's current 3d orientation. 
                  }
        \argumentb{vel}
                  {
                    \texttt{Vec3}.  The $(v_x , v_y , v_z)$ velocity of the car.
                  }
        \argumentb{omega}
                  {
                    \texttt{Vec3}.  The $(\omega_x , \omega_y , \omega_z)$ angular velocity of the car.
                  }                 
               }
      }





\class{Boostpad}
      {
        \attribute{index}
                  {
                    Integer.  The index of the boost pad in the list of boost pads.
                  }
        \attribute{pos}
                  {
                    \texttt{Vec3}. The $(x,y,z)$ position of the boost pad.
                  }
        \attribute{is\_active}
                  {
                    Boolean.  True if the boost is currently available to be picked up.
                  }
        \attribute{timer}
                  {
                    Float.  The time until \texttt{is\_active} becomes True again.
                  }
        
      }


















      
      





































  
  





\end{flushleft}
\end{document}
